The effect of climate forcing on numerical simulations of the Cordilleran ice sheet at the Last Glacial Maximum

### 2014-04-01 cordillera-climate.tex
Rework discussion of precipitation changes

Our representation of climate history by constant temperature offsets is voluntarily simplistic. To better understand the transient character of the LGM Cordilleran ice sheet, time-dependent palaeo-climate forcing would be needed. Although it is clear that past temperature changes over the region were neither homogeneous nor constant in time, their patterns are not trivial and may potentially display a~strong inter-dependence with the evolution of the Cordilleran and Laurentide ice sheets. As previously discussed, potential effects of the growing ice-sheet on precipitation changes are not included in our model. Although the ice sheet interior likely became dryer, precipitation may increased along part of the margin where the presence of ice imposed ascending winds. In this context, using a~GCM of intermediate complexity \citep{yoshimori-etal-2001,calov-etal-2002,abeouchi-etal-2007,charbit-etal-2013} may help producing more westerly-centred ice configurations than those presented here (Fig.~\ref{fig:best}).

>>>>

Our representation of climate history by constant temperature offsets is voluntarily simplistic. To better understand the transient character of the LGM Cordilleran ice sheet, time-dependent palaeo-climate forcing would be needed. Although it is clear that past temperature changes over the region were neither homogeneous nor constant in time, their patterns are not trivial and may potentially display a~strong inter-dependence with the evolution of the Cordilleran and Laurentide ice sheets. As previously discussed, potential effects of the growing ice-sheet on precipitation changes are not included in our model. These changes likely consist of a reduction of precipitation in continental regions and in the ice sheet interior, and an increase of precipitation along part of the margin where the presence of ice imposed ascending winds, which could result in a thinner ice sheet than modelled here. In addition, the final position of the eastern ice margin is largely controlled by its advance rate through the run. Therefore, precipitation shadowing effects may have resulted in more similar ice-sheet configurations if they were included in the model. Although using a GCM of intermediate complexity \citep{yoshimori-etal-2001,calov-etal-2002,abeouchi-etal-2007,charbit-etal-2013} may represent a first step towards including ice sheet feedback on climate, their spatial resolution does not allow for accurate resolution of orographic precipitation changes in a region as mountainous as the North American Cordillera.
